---
title: "p8015_hw5_ax2173"
output: github_document
---

```{r}  
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = '90%'
)

theme_set(theme_classic() + theme(legend.position = 'bottom'))

options(
  ggplot2.continous.colour = 'viridis_d',
  ggplot2.continous.fill = 'viridis_d'
)

scalr_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1


## Problem 2

Import data. 

```{r}
homicide_df = read_csv("./data/homicide-data.csv")
```

* There are some descriptions about the raw data:
  * There are totally `r ncol(homicide_df)` columns.
  * There are totally `r nrow(homicide_df)` rows.
  * In this dataframe, these variables can be found: `r colnames(homicide_df)`.

Create a city_state variable.

```{r}
homicide_df %>% 
  mutate(city_state = str_c(city, ', ',state))
```

Summarize within cities to obtain the total number of homicides and the number of unsolved homicides.

```{r}
homicide_df %>%  
  mutate(
    homicide = ifelse(disposition == "Closed without arrest", 1, 0),
    unsolved_homicides = ifelse(disposition == "Open/No arrest", 1, 0)
    ) %>% 
  group_by(city) %>% 
  summarize(
    n_homicides = sum(homicide),
    n_unsolved_homicides = sum(unsolved_homicides),
   ) %>% 
  knitr::kable()
```

For the city of Baltimore, MD, estimate the proportion of homicides that are unsolved.

```{r}
prop_of_unsolved_homicides = 
  prop.test(1673, 1673 + 152, alternative = c("two.sided"), conf.level = 0.95) %>% 
  broom::tidy()
```

* For the city of Baltimore, MD, the estimated proportion of homicides that are unsolved is `r prop_of_unsolved_homicides[['estimate']]`.
* The confidence interval is (`r prop_of_unsolved_homicides[['conf.low']]`, `r prop_of_unsolved_homicides[['conf.high']]`)

## Problem 3

